---
title: "Coursework Template"
subtitle: 'MSc in Statistics 2025/26, Imperial College London'
author: "Nikhil Pant"
format:
  html:
    toc: true
    highlight: tango
    self-contained: true
    df-print: paged
  pdf: default
format-links: false
bibliography: "MSc_Statistics_coursework_template_quarto.bib" 
---

<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>


```{r setup, include = FALSE, tidy=TRUE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
include_solutions <- TRUE
```
```{r setup2, include=FALSE, tidy=TRUE}
require(rmarkdown)
require(knitr)
require(kableExtra)
require(dplyr)
# Put any library imports and other preamble here.

```

```{r}
#| warning: false
#| echo: false
library(palmerpenguins)
```

# Palmer Penguins Analysis
### Introduction
We want to look at the general relationship between penguin bill length and depth,
using the Palmer Penguins dataset. Let's first look at the basic relationship 
between bill length and depth.
```{r}
#| echo: false
plot(
  x = penguins$bill_length_mm,
  y = penguins$bill_depth_mm,
  main = "Penguin bill dimensions",
  sub = "Data source: Palmer Penguins"
)
```

### Species Level Analysis
Given the lack of a clear relationship when looking at overall bill length 
and depth, we instead define the following function to examine mean bill
length and depth by species.
```{r}
species_mean <- function() {
  spec_df <- penguins %>% group_by(species) %>% summarise(
    avg_bill_length_mm = mean(bill_length_mm, na.rm = TRUE),
    avg_flipper_length_mm = mean(flipper_length_mm, na.rm = TRUE)
  )
  spec_df
}

spec_table <- species_mean()
```
This generates the following table:
```{r}
#| echo: false
knitr::kable(round(spec_table, 2), col.names = c("Species","Avg Bill Length (mm)", "Avg Flipper Length (mm)"))
```


